\logremark{-1:16}{\herobuild}{Bought very little regen to lane top. Buy only the Ring  of Protection and delay finishing the Basilius, get additional tangoes or/and a salve}
\logremark{0:56}{\execution}{Can go for an additional Quill Spray hit on PL (lots of stacks)}
\logremark{1:02}{\mechanics}{Missed deny}
\logremark{1:09}{\mechanics}{Missed lasthit (stood too far, am can deny)}
\logremark{1:13}{\mechanics}{Missed lasthit (went for deny hit, weaver missed)}
\logremark{1:13}{\decision}{Missed good opportunity for sidepull (the hard camp). PL isn’t contesting, lane is pushed}
\logremark{1:19}{\execution}{Drew tower aggro, didn’t shift it off after (dont rightclick the AM immediately, walk close first. Deny click a creep to drop aggro)}
\logremark{1:41}{\decision }{Stayed to fight at tower – sidepull the hard camp}
\logremark{1:51}{\mechanics}{Missed deny}
\logremark{1:53}{\decision}{Went for lasthit in the tower – took a lot of damage. (and even got denied)}
\logremark{1:56}{\mechanics}{Missed lasthit (overestimated damage)}
\logremark{2:09}{\mechanics}{Missed deny (overestimated damage)}
\logremark{2:41}{\mechanics}{Missed deny (didnt try, writing chat?)}
\logremark{2:51}{\mechanics}{Took unnecessary tower damage (underestimated range, tried to harass)}
\logremark{4:17}{\herobuild}{Prioritised upgrading boots. Should instead get Ring of Health early, no regen left over}
\logremark{5:07}{\mechanics}{Missed deny(backed unnecessarily)}
\logremark{5:38}{\decision}{Pushing the lane – should instead try to deny and pull it back}
\logremark{5:53}{\decision}{Playing dangerously aggressive – would die if AM blinks in}
\logremark{6:24}{\efficiency}{Healing at fountain on Strength tread – switch to Agi.}
\logremark{6:45}{\efficiency}{Unnecessary TP to lane (save the gold, Weaver can keep the lane solo, )}
\logremark{7:36}{\mechanics}{Unnecessary tower damage}
\logremark{7:59}{\decision}{Dangerous going forward – could die to lance+ AM blink in (didn’t check PL to see he has no mana)}
\logremark{9:12}{\information}{Important! Bad Camera movement! Miss pathing of enemies, lets PL escape}
\logremark{9:40}{\mechanics}{Walk back close to the AM – risking harassment, losing mana}
\logremark{9:55}{\decision}{Stayed in lane without mana, low HP, no regen – just back to base.}
\logremark{10:54}{\execution}{Pushing with Ring of Basilius turned off – turn on to make creeps more tanky}
\logremark{11:09}{\execution}{Important! Didn’t drop tower aggro, leads to death}
\logremark{13:01}{\decision}{Missed opportunity to by TP at sideshop}
\logremark{13:24}{\mechanics}{Missed lasthit (quill spray early, }
\logremark{13:34}{\execution}{Pushing with Ring of Basilius turned off}
\logremark{13:40}{\information}{Bad camera placement – cant see your pudge, who is walking in}
\logremark{13:42}{\execution}{Backing from pudge  - too far to follow up for dark seer}
\logremark{13:48}{\execution}{Important! Bad pathing – keep running forward while Ogre is focused. Should immediately turn and run.}
\logremark{13:52}{\execution}{Suboptimal pathing – juke into the trees instead of walking out}
\logremark{14:42}{\decision }{Important! Slow movement by walking to secret shop – TP to any lane, either buy vanguard at sideshop or send courier to mid. Top = Bot > Mid > Walking}
\logremark{14:42}{\decision}{Missed opportunity to by TP at base}
\logremark{16:16}{\execution}{Using mana on creep when low – conserve for the fight(2x quill spray).}
\logremark{16:50}{\execution}{Could turn to hit the PL}
\logremark{17:02}{\mechanics}{Hitting tower on Int treads, should switch to Str}
\logremark{18:10}{\execution}{Important! Keep fighting after killing PL. Hard to kill AM, reinforcements from tower.}
\logremark{19:00}{\decision}{Missed opportunity to by TP at base}
\logremark{20:51}{\information}{Didnt watch the fight – little information on what is happening}
\logremark{21:31}{\decision}{Stay and push until enemies respawn -  should back out before}
\logremark{22:32}{\decision}{Tabbed out too long – stand in base for 17 seconds after respawn}
\logremark{22:50}{\decision}{Missed opportunity to buy 2nd TP at base (TP out to mid, no shop there. Want to TP top at 2350)}
\logremark{23:15}{\decision}{Wasted dust (unlikely that riki just stands there. Also no way to kill, Riki can purge the Dust with Diffusal Blade)}
\logremark{23:23}{\efficiency}{Could toggle Treads to Int when using Quillspray on neutrals}
\logremark{24:11}{\mechanics}{Missed lasthit (overestimated damage)}
\logremark{24:46}{\mechanics}{Missed lasthit (overestimated damage)}
\logremark{24:51}{\mechanics}{Missed lasthit (focus wrong creep)}
\logremark{24:53}{\mechanics}{Missed lasthit (left creepwave early)}
\logremark{24:55}{\mechanics}{Missed lasthit (left creepwave early)}
\logremark{25:09}{\efficiency}{Unnecessary Dust (sentry get placed before)}
\logremark{25:28}{\execution}{Pushing with Ring of Basilius turned off}
\logremark{26:05}{\decision}{Important! Went to dive into base – could finish off the melee barracks}
\logremark{27:10}{\efficiency}{Stood in base after respawn – decide items quicker and move}
\logremark{27:22}{\efficiency}{Walk mid – lane is pushed, nothing to do. Go bottom instead}
\logremark{27:31}{\efficiency}{Tab out too long – hero is idle for 5 seconds}
\logremark{28:30}{\decision}{Went to farm jungle – instead push bottom, frontline to enter dangerous space.}
\logremark{29:00}{\mechanics}{Missed lasthit (overestimated damage)}
\logremark{29:18}{\efficiency}{Suboptimal pathing – can walk directly to mid.}
\logremark{30:34}{\decision}{Go back into fight with low health – just back and heal.}
\logremark{33:20}{\decision}{Scared to walk through wall – 4 dead, want to hit barracks.}
\logremark{35:10}{\decision}{Keep roshing without Bloodseeker and Weaver – need to back out}
\logremark{36:25}{\efficiency}{didnt’t buy items while dead – delays moving out by 13 seconds }
\logremark{39:45}{\mechanics}{Missed 2 lasthits (walked away/bad quill spray)}
\logremark{39:57}{\mechanics}{Missed lasthit (didnt cast quill spray)}
\logremark{40:56}{\execution}{Didnt cast quillspray after silence ends – missed 2 stacks}
\logremark{41:00}{\decision}{Go into the fight after tower dies – fighting 4v5 without weaver, rather back off}
\logremark{43:11}{\mechanics}{Missed lasthit (didnt cast quill spray)}
\logremark{43:31}{\mechanics}{Missed lasthit (overestimated damage)}
\logremark{43:46}{\mechanics}{Missed lasthit (switched target)}
\logremark{43:48}{\mechanics}{Missed lasthit (hit early)}
\logremark{43:49}{\mechanics}{Missed lasthit (hit early)}
\logremark{43:57}{\decision}{Pushing highground with 3 heroes – wait until pudge/bloodseeker join}
\logremark{44:37}{\decision}{Show in aggressive position! 3 allies dead}
\logremark{46:00}{\efficiency}{Tabbed out too long – stand in base for 5 seconds after respawn}
\logremark{46:36}{\decision}{Went alone into lost fight, rather push out a bottom/ set up in base}
\logremark{48:07}{\efficiency}{Slow to move out – stand in base for 4 seconds}
\logremark{49:00}{\decision}{Pushed in through mid – instead go bottom to hit barracks, so other lanes can push in}
\logremark{49:16}{\execution}{Late BKB – Use at 4913 so mana doesn’t get burned by AM illusions}
\logremark{49:53}{\efficiency}{Didn’t switch Treads to Int to TP out earlier}
\logremark{51:15}{\mechanics}{Missed lasthit (underestimated Quill Spray range)}
\logremark{51:17}{\mechanics}{Missed lasthit (hit early)}
\logremark{51:19}{\mechanics}{Missed lasthit (hit early)}
\logremark{51:21}{\mechanics}{Missed lasthit (hit wrong creep)}
\logremark{51:22}{\mechanics}{Missed lasthit (hit wrong creep)}
\logremark{51:24}{\mechanics}{Missed lasthit (hit early)}
\logremark{51:26}{\mechanics}{Missed lasthit (cast quill spray early)}
\logremark{51:27}{\mechanics}{Missed lasthit (switched target)}
\logremark{51:28}{\mechanics}{Missed lasthit (cast quill spray early)}
\logremark{52:05}{\decision}{Hitting creeps instead of barracks – no enemies nearby, 3 dead}
\logremark{52:23}{\execution}{Didnt cast Goo to maximize Warpath stacks}
\logremark{52:40}{\execution}{Didnt immediately back after killing the barracks (lost 2 seconds to walking around, then more to hitting DS)}
\logremark{54:05}{\decision}{AFK for too long – stood in base for 35 seconds}
\logremark{54:47}{\decision}{Pushing enemy base with 3 heroes (and 1 far behind) – wait until all are grouped, this gives the enemies a chance to fight}
